---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xciter

![Haywire](https://img.shields.io/badge/status-haywire-red)
![MaybeNotHelpful](https://img.shields.io/badge/NeverMind-MaybeNotHelpful-green)

This package focuses solely on "extra" functions related to citeing bibliography 
items such as processing .bib files to get citation keys, processing BiBtex keys to get inline citations, etc.  We
are calling it "extra" because we rely heavily on [`rbbt`](https://github.com/paleolimbot/rbbt) and standard
`rmarkdown::render` magic to almost everything we need to do. Some functions for rendering citation keys
as inline references wrap calls to `pandoc` so that needs to be installed. If you have Rstudion you likely have it already.

This package deals with a few problems as follows:

  - Identify all citation keys in documents and confirm their presence in a specified .bib file.
  - Highlight citation keys that do not match and suggest the closest matching keys from the .bib file.
  - Provide workarounds for citation handling in interactive tables [(DT)](https://github.com/rstudio/DT) and other HTML 
  outputs where standard citation rendering in R Markdown and Quarto may fail.

## Installation

You can install the development version of xciter from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
pak::pkg_install("NewGraphEnvironment/xciter")
```

## Example

This is a basic example of subbing citation keys for inline references within a table so that it can
be rendered as is after the changes are made:

```{r example}
library(xciter)
## basic example code

path_bib <- system.file("extdata", "NewGraphEnvironment.bib", package = "xciter")
dat <- data.frame(
  id = 1:3,
  bib_keys = c(
    "Outside block quotes @busch_etal2011LandscapeLevelModela and in [@woll_etal2017SalmonEcological]",
    "This is many [@busch_etal2011LandscapeLevelModela; @woll_etal2017SalmonEcological; @kirsch_etal2014Fishinventorya]",
    "this is a failed key @key3"
  )
)
result <- xct_keys_to_inline_table_col(dat, col_format = "bib_keys", path_bib = path_bib)
print(result)
```

This is a basic example of checking if the citation keys within a bookdown document are found within a specified
`.bib` file.

```{r}
key_missing <- xct_bib_keys_missing(path_bib, "kirsch_etal2014Fishinventory")
```


<br>

This is an example of how to search for the closest match for an unmatched key.

```{r}
xct_keys_guess_match(key_missing, keys_bib = xct_bib_keys_extract(path_bib))
```

